openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Fix conflicts

@@

# Cleaning
oarch_graph |>
  rename(user = author) |>
  filter(!str_detect(user, coll("[bot]"))) ->
  oarch_graph
```

@@

```{r plot-graph-repo-user}
oarch_graph_repo_user <- tbl_graph(nodes_repos_users(oarch_graph),
                                   edges_user_to_repo(oarch_graph),
                                   directed = FALSE)

oarch_graph_repo_user |>
  ggraph(layout = "graphopt") +
  geom_edge_fan(aes(colour = contrib, alpha = n_contrib)) +
  geom_node_point(aes(colour = node_type)) +
  scale_edge_alpha(trans = "log")
```

@@

```{r plot-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph, category, tags),
                                   edges_common_users(oarch_graph))

@@

```{r plot-graph-user-user}
oarch_graph_user_user <- tbl_graph(nodes_users(oarch_graph, category), 
                                   edges_common_repos(oarch_graph))

oarch_graph_user_user |>
  mutate(degree = centrality_degree()) |>
  filter(degree > 0) |>
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = n)) +
  geom_node_point(aes(colour = category)) +
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common repositories")
```

>>>>

Q's:

1. Are there significant networks? If so, how big and how many?
  * Only one, it seems!
2. What proportion of users and repos are connected to this network?
3. What predicts membership in this network?
4. Does centrality in the network correlate with general rate of activity?
5. Who are the most central nodes in this network? Is there anything they have in common?
   * High activity?
   * Certain platforms/categories/languages?

@@

# Cleaning
oarch_graph |>
  rename(user = author) |>
  # Remove non-human users
  filter(!str_detect(user, coll("[bot]"))) |>
  filter(!user %in% c("ghost", "codecov-io", "coveralls", "codecov-commenter",
                      "gitter-badger", "dependabot-support")) |>
  # Remove big, non-archaeology projects that flood the network
  filter(!repo %in% c("Stellarium/stellarium", 
                     "opengisch/QField",
                     "lutraconsulting/input")) ->
  oarch_graph
```

@@

```{r plot-graph-repo-user}
oarch_graph_repo_user <- tbl_graph(nodes_repos_users(oarch_graph),
                                   edges_user_to_repo(oarch_graph))

g_repo_user <- oarch_graph_repo_user |>
  ggraph(layout = "graphopt") +
  geom_edge_fan(aes(colour = contrib, alpha = n_contrib)) +
  geom_node_point(aes(colour = node_type)) +
  scale_edge_alpha(trans = "log")

#g_repo_user
girafe(g_repo_user)
```

@@

```{r plot-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph, category),
                                   edges_common_users(oarch_graph),
                                   directed = FALSE)

@@

```{r graph-user-user}
oarch_graph_user_user <- tbl_graph(
  nodes = nodes_users(oarch_graph), 
  edges = edges_common_repos(oarch_graph),
  directed = FALSE
)
```

```{r summary-graph-user-user}
oarch_graph_user_user |>
  mutate(degree = centrality_degree(), 
         betweenness = centrality_betweenness(weights = n), 
         strength = centrality_degree(weights = n)) |>
  filter(degree > 0) |> 
  data.frame() |> 
  View()
```

```{r plot-graph-user-user}
oarch_graph_user_user |>
  mutate(degree = centrality_degree(), strength = centrality_degree(weights = n)) |>
  filter(degree > 0) |>
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = n)) +
  # geom_node_point(aes(colour = category)) +
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common repositories")
```
